%!TEX TS-program = pdflatexmk

% Copyright 2020 Martin Scheidt (Attribution 4.0 International, CC-BY 4.0)
% You are free to copy and redistribute the material in any medium or format. You are free to remix, transform, and build upon the material for any purpose, even commercially. You must give appropriate credit, provide a link to the license, and indicate if changes were made. You may not apply legal terms or technological measures that legally restrict others from doing anything the license permits. No warranties are given.

\documentclass[
  % draft,
  paper=a4,
  version=3.25,
  pagesize=pdftex,
  twoside=false,
  DIV=12,
  headinclude=true,
  footinclude=false,
  toc=listof,
]{scrartcl}

\def\ROOT{./..}
\input{\ROOT/src/handbook_header.tex}

\begin{document}
  \selectlanguage{ngerman} % currently supported: english, ngerman

  \thispagestyle{empty}
  \begin{center}
    \IfLanguage{english}{\Large Set List}
    \IfLanguage{ngerman}{\Large Liste für ein Set}
    \\
    handbook - 16/8 sheets of normal paper
    protocol - hand-full of normal paper
    predefined track with plattforms - 4 sheets of WHITE thick paper (appr. 200g/sqm)
    plain track - 3 sheets of WHITE thick paper (appr. 200g/sqm)
    plattforms - 1 sheets of WHITE thick paper (appr. 200g/sqm)
    distant signals - 1 sheets of WHITE thick paper (appr. 200g/sqm)
    block signals - 1 sheets of WHITE thick paper (appr. 200g/sqm)
    route signals - 1 sheets of WHITE thick paper (appr. 200g/sqm)
    clearing points - 1 sheets of WHITE thick paper (appr. 200g/sqm)

    turnout base - 3 sheets of WHITE thick paper (appr. 200g/sqm)
    turnout point - 3 sheets of WHITE thick paper (appr. 200g/sqm)
                  - 3 brass fastener
    turnout token - 1 sheets of WHITE thick paper (appr. 200g/sqm)


    local train - 2 sheets of YELLOW thick paper (appr. 200g/sqm)
    fast train - 2 sheets of RED thick paper (appr. 200g/sqm)
    freight train  - 3 sheets of BLUE thick paper (appr. 200g/sqm)
    - 2 double tally counters (if you find only single tally counters, thats ok)
    
    \vfil\normalsize
  \end{center}
\end{document}