%!TEX TS-program = pdflatexmk
%!TEX root = ../handbook.tex

% Copyright 2018 Martin Scheidt (ISC license)
% Permission to use, copy, modify, and/or distribute this file for any purpose with or without fee is hereby granted, provided that the above copyright notice and this permission notice appear in all copies.
\chapter*{\IfLanguage{english}{Aim and Materials}\IfLanguage{ngerman}{Ziel und Materialien}}

\noindent
\IfLanguage{english}{The aim of the learning game is to simulate and experience the driving dynamics of trains in the context of block division. This requires:}
\IfLanguage{ngerman}{Ziel des Lernspieles ist die Fahrdynamik von Zügen im Zusammenhang mit Blockteilung zu simulieren und zu erfahren. Dafür wird benötigt:}
\begin{itemize}
  \IfLanguage{english}{
    \item two trains with different driving dynamics
    \item a track consisting of spaces
    \item train berths
    \item signals for block division
    \item if necessary, turnouts
  }
  \IfLanguage{ngerman}{
    \item zwei Züge mit unterschiedlicher Fahrdynamik
    \item eine Strecke, bestehend aus Spielfeldern
    \item Halteplätze für die Züge
    \item Signale für die Blockteilung
    \item ggf. Weichen
  }
\end{itemize}
\IfLanguage{english}{Real continuous dimensions time ($t$) and distance ($s$) are assigned to discrete units of rounds ($t$) and spaces ($s$).
Thus, the simulation is round-based in order to imitate the steps of a computer.}
\IfLanguage{ngerman}{Reale kontinuierliche Größen Zeit ($t$) und Strecke ($s$) werden dabei in diskrete Einheiten von Runden ($t$) und Felder ($s$) eingeteilt.
Die Simulation erfolgt also Rundenbasiert, um im Schrittverfahren einen Computer nachzuahmen.}

\vspace*{\fill}

\IfLanguage{english}{
  {\noindent\large Version \vhCurrentVersion\ from \vhCurrentDate } \\[0.3cm]
  \ccLogo \ccAttribution ~This work is licensed under a Creative Commons License (CC BY 4.0).
}
\IfLanguage{ngerman}{
  {\noindent\large Version \vhCurrentVersion\ vom \vhCurrentDate } \\[0.3cm]
  \ccLogo \ccAttribution ~Dieses Werk steht unter der Creative Commons Lizens (CC BY 4.0).
}